\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payout Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-19 latex/article.tex
alternative

    \item \textbf{Put-Call Parity Flexibility:} The implementation allows for two 
    alternative approaches:
    \begin{itemize}
        \item Direct use of both calls and puts as separate instruments
        \item Expressing puts through calls and spot positions using put-call parity
    \end{itemize}
    This flexibility enables optimization of the portfolio structure based on market 
    conditions and transaction costs.
\end{enumerate}

@@

where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) 
are option weights. The optimal weights are found by solving the regularized least 
squares problem with either L2 (Ridge) or L1 (Lasso) regularization:

\begin{equation}
\min_{\boldsymbol{\theta}} 
    \int_{S_{\min}}^{S_{\max}} 
        \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
    \gamma \|\boldsymbol{\theta}\|_p^p
\end{equation}

where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
the position weights, \( \gamma \) is the regularization parameter, 
\( S_{\min}, S_{\max} \) define the approximation domain, and \( p \) determines
the type of regularization. The L2 norm (\(p=2\)) promotes smoother weight 
distributions, while the L1 norm (\(p=1\)) tends to produce sparse solutions by 
setting some weights exactly to zero, which can be beneficial when portfolio 
simplicity is important consideration.

Discretizing the integral and using matrix notation, we solve:

\begin{equation}
\boldsymbol{\theta}^* = 
    \argmin_{\boldsymbol{\theta}} 
        \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + 
        \gamma \|\boldsymbol{\theta}\|_p^p
\end{equation}

@@

\subsection{Numerical Implementation}
The discrete optimization problem with L2 regularization has a closed-form solution:
\begin{equation}
\boldsymbol{\theta}^* = 
    (\mathbf{A}^\top \mathbf{A} + \gamma \mathbf{I})^{-1} 
    \mathbf{A}^\top \mathbf{b}
\end{equation}

where $\mathbf{A} \in \mathbb{R}^{N \times (n+m+1)}$ represents the matrix of basis 
payoffs, $\mathbf{b} \in \mathbb{R}^N$ contains target payoff values, $\gamma$ 
controls solution smoothness through regularization, and $\mathbf{I}$ denotes the 
identity matrix. Evaluation points $\{S_k\}$ are typically distributed around the 
current spot price to emphasize approximation accuracy in relevant price regions. 
The L1-regularized problem is solved using iterative optimization methods.

>>>>

    \item \textbf{Put-Call Parity Flexibility:} The implementation supports both direct 
    use of calls and puts as separate instruments, as well as expressing puts through 
    calls and spot positions using put-call parity. This approach provides flexibility 
    in portfolio construction while maintaining mathematical equivalence.
    This flexibility enables optimization of the portfolio structure based on market 
    conditions.
\end{enumerate}

@@

where \( \lambda \) represents the spot position, \( \alpha_i \) and \( \beta_j \) 
are option weights. The optimal weights are found by solving the regularized least 
squares problem with L2 (Ridge) regularization:

\begin{equation}
\min_{\boldsymbol{\theta}} 
    \int_{S_{\min}}^{S_{\max}} 
        \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
    \gamma \|\boldsymbol{\theta}\|_2^2
\end{equation}

where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
the position weights, \( \gamma \) is the regularization parameter, and 
\( S_{\min}, S_{\max} \) define the approximation domain. The L2 norm promotes 
smoother weight distributions, providing stability to the solution.

Discretizing the integral and using matrix notation, we obtain:

\begin{equation}
\boldsymbol{\theta}^* = 
    \argmin_{\boldsymbol{\theta}} 
        \|\mathbf{A}\boldsymbol{\theta} - \mathbf{b}\|_2^2 + 
        \gamma \|\boldsymbol{\theta}\|_2^2
\end{equation}

@@

This quadratic optimization problem admits an analytical solution:
\begin{equation}
\boldsymbol{\theta}^* = 
    (\mathbf{A}^\top \mathbf{A} + \gamma \mathbf{I})^{-1} 
    \mathbf{A}^\top \mathbf{b}
\end{equation}

\subsection{Alternative Loss Functions}
While the standard L2 loss function provides analytical tractability, alternative 
formulations may better reflect trading objectives. Two notable generalizations are:

\begin{enumerate}
    \item \textbf{L1 Regularization (Lasso):} Replacing L2 regularization term with L1 norm:
    \begin{equation}
        L(\boldsymbol{\theta}) = 
            \int_{S_{\min}}^{S_{\max}} 
                \left[ V(S) - \hat{V}(S;\boldsymbol{\theta}) \right]^2 dS + 
            \gamma \|\boldsymbol{\theta}\|_1
    \end{equation}
    This formulation tends to produce sparse solutions by setting some weights exactly 
    to zero, which can be beneficial when portfolio simplicity is important consideration.

    \item \textbf{Weighted Error Function:} Incorporating target function magnitude 
    into the error term:
    \begin{equation}
        L(\boldsymbol{\theta}) = 
            \int_{S_{\min}}^{S_{\max}} 
                V(S) \Big| V(S) - \hat{V}(S;\boldsymbol{\theta}) \Big| dS + 
            \gamma \|\boldsymbol{\theta}\|_p^p
    \end{equation}
    This formulation provides error weighting proportional to the target payout magnitude, 
    offering economic interpretation well-aligned with trading objectives. Furthermore, it 
    naturally enhances focus on regions with significant payout values, making it particularly 
    suitable for practical applications.
\end{enumerate}

However, these generalizations lose the analytical tractability of the L2 case, 
requiring numerical optimization methods for solution.

\subsection{Numerical Implementation}
The implementation leverages the analytical solution derived in the Mathematical Framework 
section for L2-regularized problems. For L1 regularization and alternative loss functions, 
numerical optimization methods are employed.
